\section*{Block 6: Requirements}

The website used for this block is a website used for our semester project. The website is used create and manage all sorts of exhibitions. 

The website is a part of an Android application to help visitors navigate around at an exhibition. Imagine an exhibition where different companies have set up booths where they can talk to the visitors. The website is used for creating the layout of an exhibition, by creating companies, their booths and create paths between all booths so it is possible to navigate around. 

Because it was a semester project we did not have any external stakeholders for this project, meaning we always had stakeholders (ourselves) on-site. However if it was a "real-life" product, it would be ideal to interview organizers of exhibitions to find out what functions they would want to have with a tool like this.

This eased the process of finding the functional requirements, as we already had a clear idea of what we wanted before we started and there were no interviews needed. Based on our application, we already knew what functionality the website should have. The website must be able to perform the following actions:

\begin{itemize}[noitemsep]
\item Create an exhibition
\item Create a company with a name and logo
\item Create different categories
\item Create a booth which is connected to a company, the booth must have a name, category and a description
\end{itemize}

The tasks analyses performed were based on how we thought the interaction with the website should be\todo{Evt visio billiede af task model}

First the organizer creates an exhibition, then they can choose to add companies, categories or booths. Adding a company means giving the company a name and a logo. The company names and categories are used when creating booths. If the organizer is creating a booth with a company that is not created yet, they will be asked to upload a logo and then the company will be created when submitting the booth.

We wanted the navigation to be simple, so we kept it all on one site with some tabs at the top, using JQuery to allow the organizers to switch between the different tools without reloading the page.