The basic idea is to map an exhibition and collect data from peoples locations and interests. Furthermore the mobile application should aid the users to get more information from the exhibition. Each booth will provide a description about what the booth is about. Events will also be made avaiable using a schedule, as well as a live feed from the exhibition.
The project is a two-part development, both a serverside, mainly for coordination and syncronization, and a mobile application for the end-user attending the exhibition. Features of both can be seen below.

\subsection*{Features}

\begin{itemize}
\item Application to load floorplan and make routes. (Administration).

\item Administration website\\
\textit{A place to insert information and location of booths.}
\end{itemize}

\subsection*{Mobile application}
The mobile application is designed for the end-user, and can load any given exhibition using the system. This will create a schdule for the user with the booths of interest is mapped. Feeds, choosen on interests and location, will also be shown in the application.

\begin{itemize}
\item NFC tag reader

\item Should read a "global" tag that binds the application to the current exhibition.

\item Should also read a "local" tag that is bound to each booth.\\
\textit{This could trigger additional information about the booth, or help you get directions to anohter booth.}
\item Time schedule of events.

\item View floorplan.

\item Feed of realtime news. A booth could for example send a realtime post to all users interested in this booth.\\
\textit{Twitter could be incorporated in this.}

\item When the application is not bound to anything, the app should show an exhibition browser that lets you search for exhibitions that you might be interested in.
\end{itemize}

\subsection*{Ideas of ways to subscribe to booths}

\begin{itemize}
\item Every booth have some categories, and when the initial NFC is read, you can choose which categories you wish to subscribe to.

\item Every booth is subscribed to from start, and the user must manually unsubscribe from everything he finds uninteresting.
\end{itemize}

\subsection*{Information that could be gathered from the users/mobile app}

\begin{itemize}
\item Density / queues ( This could be shown to the users, realtime)

\item General interests

\item Statistics of each booth\\
\textit{When a user scans a tag at a booth, the hit should be recorded. An idea is that he chooses to either get more information or get directions to another booth. Data from both can be gathered.}\citep{rtsbog}
\end{itemize}
