\section{Exhibition system}\label{sec:exhibsystem}

Our idea is to make a visit to an exhibition more informative and personalised. The system will be split up into two components, a website for the organizers of the exhibitions, allowing them to set up an exhibition and a mobile application for the attendees at the exhibition.

The mobile application should provide the user with a personalised experience of the exhibition, this could be in form of a personalised route around the exhibition and different live feeds matching their interests. These live feeds could be information about small events at different booths like: give-aways, contests, etc. The feed list is meant as a place where the booths can make themselves attractive to the visitors who are interested in them. The mobile application should also provide a schedule for larger events happening around the exhibition. The application should also have floor plan of the exhibition displaying the location of all booths allowing the user to easily navigate between the different booths. 

\subsection*{Website Application}
The website application is designed for the organizers as a tool to help set up an exhibition. From here they should be able to register the different companies attending the exhibition and make a layout of the exhibition and plot the location of the different booths. Below is listed some of the important implementations that have to be made.
\todo{Write a description to understand the website application/administration tool}
\begin{itemize}
\item Add to and edit companies at the exhibition.
\item Add and edit categories.
\item Add to and edit booths at the exhibition, including booth information and categories.
\item Tool for setting up a floor plan of the exhibition and plotting in the different booths.
\item The booths should be able to publish live feeds to the users.
\end{itemize}
\subsection*{Mobile Application}

The mobile application is designed for the visitor, and can load any given exhibition using the system. When physically entering the exhibition, the visitor has to subscribe to that specific exhibition. After subscribing to an exhibition the visitor will have to choose categories that they find interesting. 

The floor plan will show a route around the exhibition to the booths that the visitor finds interesting. The visitor can only update his location on the floor plan by registering at a booth. When registering at a booth, the visitor will be presented with additional information about the booth. 

The schedule will be filled with big events that are planned by the booths and exhibition. The visitor will also receive a live feed from booths, this will update the visitor on small current events happening at the exhibition. Below is listed some of the important implementations that have to be made.
\begin{itemize}
\item A way to register the user around the exhibition.
\item Time schedule of events
\item View floor plan, for directions around the exhibition.
\item Overview of all the feeds that will be coming from the booths that are interesting to the visitor.
\item When the application is not subscribed to any ongoing exhibitions the application should show an exhibition browser, that the visitor can use to search for exhibitions.
\end{itemize}