The purpose of the map in the application is to be used as a navigation guide for the user. The user should be able to make a customised route to different booths, The default route should be a route between all the booths that the user has subscribed to.
Ideally it should also be possible to subscribe/unsubscribe to each booth. The location of the user is detected when the user scans an \ac{nfc} tag, the \ac{nfc} tag are placed around the exhibition and at booths, to provide the user with easy location determination.

\subsection*{MapView vs Mapfragment}
Our initial thought on how to implement the map on the phone was to use the service provided by Google Maps. We knew that it could implemented on the phone because we had previously seen it being used in other applications. What we did not know, was if we could override the standard Google Maps tiles with our own custom tiles. A tile is a single picture containing a piece of the map, depending on the zoom level each tile contain a smaller piece of the actual map.\\
\todo{show what a tile looks like, side by side with Google Maps tile}
We need to implement our own custom tiles because we want to show a floor plan of a building, instead of a world map. We read the documentation provided by Google Maps\todo{cite?}, and we found that it is not possible to override the standard tiles with your own tiles to the Android MapFragment. We then thought of implementing the map with a WebView which is basically a browser inside the application, and use JavaScript to create the map. With JavaScript it is possible to override the standard tile set with your own, but the performance on the phone was horrible so we scratched the idea.
We did some research to try find a solution to our problem, we ended up with using the MapFragment and instead overriding the standard tile set we simply hide them, and only show our custom tile set.

\subsection*{Mercator projection}
Google Maps use Mercator projection, good idea to know how it works
How it works.
Side effects by using this, distortions bla bla
\todo{show a picture explaining the Mercator projection.}
What does it mean in our case?(don't know what to write)

\subsection*{Google Maps}
Explain the Google Maps API for android\\
Tile rendering, how it works?\\
Google Maps elements:\\
Polylines how to make them? how they are structured, show examples\\
Polygons how to make them? how they are structured, show examples\\
Markers how to make them? how they are structured, show examples\\
Long \& Latitude?

\subsection*{Implementation of Map} 
Explain how the tiles is loaded into the app(google map)\\
Explain how thing are loaded from the database.\\
Location stuff
	
